---
title: 'Finding fast growing firms'
author: "Maeva Braeckevelt and Brúnó Helmeczy"
output:
  html_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Executive Summary
This analysis aimed at predicting the fast growing of a firm.


```{r, include=F, message=FALSE, echo=FALSE, eval=TRUE}
setwd("C:/Users/mbrae/OneDrive/Bureau/CEU/DA3/A1/")
#### SET UP

# CLEAR MEMORY
rm(list=ls())


# Import libraries
library(haven)
library(glmnet)
library(purrr)
library(margins)
library(skimr)
library(kableExtra)
library(Hmisc)
library(cowplot)
library(gmodels) 
library(lspline)
library(sandwich)
library(modelsummary)

library(rattle)
library(caret)
library(pROC)
library(ranger)
library(rpart)
library(partykit)
library(rpart.plot)


# set working directory
data_dir <- paste0(getwd(),"/DA3_A2_Bruno_Maeva/")
SourceFunctions <- paste0("https://raw.githubusercontent.com/Maeva2408/DA3_A2_Bruno_Maeva/main/code/functions/")

# load theme and functions
source(paste0(SourceFunctions,"theme_bg.R"))
source(paste0(SourceFunctions,"da_helper_functions.R"))

data_in <- paste(data_dir,"data/clean/", sep = "/")
output <- paste0(data_dir,"output/")
create_output_if_doesnt_exist(output)
data_out <- paste(data_dir,"data/clean/", sep = "/")



###########################################################
# Import data
###########################################################

dataraw <- read_csv("https://raw.githubusercontent.com/Maeva2408/DA3_A2_Bruno_Maeva/main/data/clean/cs_bisnode_panel.csv")

data <- dataraw


# drop variables with many NAs
data <- data %>%
  select(-c(COGS, finished_prod, net_dom_sales, net_exp_sales, wages)) %>%
  filter(year !=2016)

###########################################################
# label engineering
###########################################################

# add all missing year and comp_id combinations -
# originally missing combinations will have NAs in all other columns
data <- data %>%
  complete(year, comp_id)

# generate status_alive; if sales larger than zero and not-NA, then firm is alive
data  <- data %>%
  mutate(status_alive = sales > 0 & !is.na(sales) %>%
           as.numeric(.))

# defaults in two years if there are sales in this year but no sales two years later
data <- data %>%
  group_by(comp_id) %>%
  mutate(default = ((status_alive == 1) & (lead(status_alive, 2) == 0)) %>%
           as.numeric(.),
         CAGR = ifelse( ( (is.na(lead(sales, 2))) & (status_alive == 1) ),
                             0,((lead(sales, 2) / sales )^(1/2) - 1)*100) ) %>%
  ungroup()

data <- data %>% mutate(
  HyperGrowth = CAGR >= 30) %>% 
  filter(year <=2013)



```

# Introduction

This analysis aimed at predicting the fast growth of firms between 2012 and 2014. This analysis could help an investor to decide to invest in a certain company or not.
The data we used was created by Bisnode, a major European business information company. The original dataset, bisnode-firms, contains the entire population of companies between 2005 and 2016 in Manufacturing (Electrical equiment, Motor vehicles, etc) and services (Accommodation and food and beverage services activities).

# Data

The first step of this analysis was to define fast growth. To do so, we used the compound annual growth rate formula. 

CAGR = (Vfinal/Vbegin)^1/t - 1 


t being the time in years, we defined it as 2. 
It seems logic for us that if an investor took interest in a firm, he will be able only to invest the year later.
Vbegin is the Sales (€) in the year ongoing
Vfinal is the Sales (€) in the year +2

we converted in percentage.
we defined any firm that have a % CAGR of bigger or equal at 30% in two years as a fast growing firm, it means that they growth for 70% in two years.

Our sample is defined as 
- Firms still in business in 2012
- Firms that have sales between 10 000€ and 10 millions €

Our fast growing firms are compound annual growth percentage bigger or equal at 30% in two year

Before cleaning for missing values, we end up with 17726 rows.


```{r, eval=TRUE, echo=FALSE, results='asis'}


```


```{r, eval=TRUE, echo=FALSE, results='asis'}

```


```{r, eval=TRUE, echo=FALSE, results='asis'}



```




```{r, include=F, message=FALSE, echo=FALSE, eval=TRUE}

```





```{r, eval=TRUE, echo=FALSE, results='asis', warning= FALSE}

```

## Lasso


```{r, include=F, message=FALSE, echo=FALSE, eval=TRUE}


```

## Random forest
```{r, include=F, message=FALSE, echo=FALSE, eval=TRUE}

```


```{r, include=F, message=FALSE, echo=FALSE, eval=TRUE}

```



```{r, include=F, message=FALSE, echo=FALSE, eval=TRUE}


```


```{r, eval=TRUE, echo=FALSE, results='asis'}

```



```{r, eval=TRUE, echo=FALSE, results='asis'}

```


# Conclusion / Summary

